---
title: "Assignment – Web APIs"
author: "Wiktoria Gnojek"
date: "10/24/2021"
output:
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis. 

You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

**Installing the Library(s)**
```{r}
library(jsonlite)
library(httr)
```
**API Key Created**
```{r}
key <- "Lm652PALZ1UL10AmoCcyDVtxI6DrXiZa"
```
**New York Times API**

Movie Reviews API

I will be using the New York Times Movie Reviews API, url to overview page; https://developer.nytimes.com/docs/movie-reviews-api/1/overview

Overview:

Search New York Times movie reviews by keyword and opening date and filter by Critics' Picks.

**Loading the Data**

Important to note, I chose a type of picks, offset of 20, and order by; opening date. 

URL to this portion; https://developer.nytimes.com/docs/movie-reviews-api/1/routes/reviews/%7Btype%7D.json/get
```{r}
url <- paste0("https://api.nytimes.com/svc/movies/v2/reviews/picks.json?offset=20&order=by-opening-date&api-key=",key)
movie_reviews <- GET(url)
# checking status
movie_reviews$status_code
```
**Json Data**
```{r}
json_data <- fromJSON(url)
```
**Converting to Data Frame**

Below you will see two chunks of code. The first one is loading the chosen data with a regular data frame function. This data isn't yet organized, but is checking of the portion of the assignment. 

Next, you will see the same data but with a few transformation functions as well as listed in a cleaner data table format. i also looked at frequency per byline. 
```{r}
json_data <- json_data$results
as.data.frame(json_data)
```
**Data Frame Transformations**
```{r}
library(plyr)
library(dplyr)
library(tidyr)
library(DT)
json_data %>%
  select(
display_title, mpaa_rating, critics_pick, byline, headline, summary_short) %>%
  arrange(desc(byline)) %>%
  datatable()
## Frequency by byline
table(json_data$byline)
```

